\rhead{\textit{Functional and Non-Functional Requirements}}
\lhead{}

\subsection{Functional Requirements}
\begin{itemize}
	\item {Profile Management:
	\begin{itemize}
		\item Login (with email, facebook and google);
		\item Logout;
		\item Modify personal information;
		\item Modify passwor;
		\item Forgot password;
		\item Save user email and password;
	\end{itemize}
	}
	\item Learning ASL Management:
	\begin{itemize}
		\item Learn ASL Alphabet;
		\item Learn ASL Words;
		\item Save Words Learned.
	\end{itemize} 
	\item Communication Management:
	\begin{itemize}
		\item Text to Speech;
		\item Speech to Text.
	\end{itemize}
	\item VideoCall Management.
\end{itemize}

\subsection{Non-Functional Requirements}
The application will be used by users with a varied level of technological background, therefore, the goal is to comply with the following non-functional requirements:
\begin{itemize}
	\item \textbf{Usability}:
	The interfaces have been designed to be fun but at the same time intuitive. The expert user should not get bored, while those who know less should not be in trouble. The user must be able to intuitively recognize which commands to perform to complete the desired actions, starting from the first use.
	\item \textbf{Performance}:
	The system will respond quickly to user requests.
	\item \textbf {Reliability}:
	The system will handle irregular and incorrect inputs and will alert them to the user without interfering with the normal execution of the program. it is necessary to prevent the system from creating damage due to failures. This thanks to information screens that will report exactly the mistake made
	and how to correct it.
	\item \textbf{Security and protection of legal aspects}:
	The data stored and managed by the system will be adequately protected from all risks related to the holding and the possible loss of data. This is thanks to the use of the online cloud provided by Google, Firebase, which will handle all aspects of data security and persistence.
	\item \textbf{Modularity}:
	The system will be modular, in order to make the addition or elimination of functionality simple if the functional requirements change over time.
	\item \textbf{Constraints}:
	The development of services for end users is expected using mobile technologies.
\end{itemize}